Basic Parameter estimation of Binary Neutron Star Systems by the Advanced LIGO/Virgo Network

### 2013-05-28 doc/paper.tex
finished addressing tysons comments, updating text and figures, and finalizing results with the completed runs

Within the next five years, the Advanced LIGO/Virgo network will have reached a sensitivity sufficient to enable the routine
 detection of gravitational waves.  Beyond the initial detection, the scientific promise of these instruments relies the 
 parameter estimation techniques being currently developed.  The majority of this effort has been towards the detection
   and characterization of gravitational waves from compact binary coalescence, i.e. the coalescence of black holes and/or 
   neutron stars.  While several previous studies have focused on the parameter estimation abilities of advanced detectors, 
   the majority have relied on approximation techniques such as the Fisher Matrix.  Here, we report the statistical 
   uncertainties that will be achievable, in practice, using the parameter estimation techniques which will be applied to 
   detections of binary neutron star systems.  We find the recovery of the individual masses to be within fractionally within 
   10\% at the 65\% confidence level for equal-mass systems, and within 2\% for unequal-mass systems.
     We also report the average uncertainties on the sky-locations, luminosity distance, and orbital inclinations of randomly 
     distributed sources that can be achieved by different network configurations. \carl{[PUT IN SA VALUES FOR SKY LOCATION]}
\end{abstract}

@@

Finally, note that the power-spectral density that defines the inner product \eqref{innerProduct} is simply 
the time-averaged sensitivity of a given detector to a specific frequency.  Ignoring non-Gaussian glitches,
 any stretch of data should contain a specific noise realization drawn from a Gaussian colored by the PSD.
   However, what we are interested in is not the parameter estimation that can occur in a specific draw
    from this probability of noises, but the uncertainties averaged over all possible noise
     realizations.\footnote{Similarly to how the Fisher matrix formalism can provide the Cramer-Rao bound averaged over
     all noise realizations} Since our noise model is assumed to be Gaussian, it is unnecessary to recover the
      parameters from a large sample of identical waveforms in different noise; we can simply assume the 
      noise \emph{is} the mean defined by the power-spectral density.  This ``zero-noise'' parameter estimation
       provides a statistical statement on the measurable uncertainties, and is what is reported here.  In Section
        \ref{noiseSection} we provide an example of parameter estimation in several non-zero noise realizations
compared to the zero-noise equivelant.

@@

\begin{figure}[h!]
  \centering
 \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{1414masses2D.pdf}
 \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.  The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual component masses of the binary ($M_1$ and $M_2$).  In the $\chmass$-$q$ space, the posterior would resemble a Gaussian if not for the limitation of $q \leq 1$.  The presence of the $q$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.  When projected as 1D marginalized posteriors, the component masses resemble the posterior PDFs shown in figure \ref{metaMassPDFs}.}
  \label{1414masses}
\end{figure}

\begin{figure}[h!]
  \centering
 \includegraphics[trim=0cm 0cm 2cm 0cm, clip=false,scale=0.56]{125masses2D.pdf}
 \caption{Similar to Figure~\ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.  The unequal mass ratio displaces the posterior PDFs from the $q \leq 1$ present in the equal mass case, yielding a Gaussian PDF in both the $\chmass$-$q$ and $M_1$-$M_2$ spaces.}
  \label{125masses}
\end{figure}

\begin{figure*}[ht!]
  \centering
 \includegraphics[trim=2cm 0cm 2cm 0cm, clip=false,scale=0.7]{newMasses.pdf}
 \caption{Mass PDFs for the four BNS systems, averaged over each of the 40 injections.  The average is reported since, in practice, there was quantitatively no difference between the recovered PDFs for different systems with identical masses and SNRs.  Notice how the PDFs for systems with identical mass ratios but different total masses are identical when normalized to the true total mass.}
  \label{metaMassPDFs}
\end{figure*}

@@

To condense the results into a single figure of merit, we average the 1-dimensional mass PDFs into a single 
posterior probability for system.  See Figure~\ref{metaMassPDFs}.  Notice how when averaged and
 normalized to the injected values, the recovery of the component masses depends only on the mass ratio.  
 Furthermore, for systems of equal masses, the posterior barely extends beyond 15\% of the injected values.  
 If one assumes that the threshold between black
   holes and neutron stars lies at approximately $3M_{\odot}$ \carl{[CITE WILL]}, then it might be assumed that
   the mass recovery would allow one to discriminate between black holes and neutron stars.

@@

\begin{figure}[h!]
  \centering
 \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.8]{distIota2D.pdf}
 \caption{Typical marginalized 2D mass PDFs for luminosity distance $D$ and orbital inclination $\iota$. }
 \label{distIotaPDF}
\end{figure}

Binary neutron star systems (along with neutron star/black hole systems) are one of the best candidates for progenitors of short gamma-ray bursts \carl{CITE}.  After merger, the remnant is believed to emit the burst along the axis of orbital angular momentum, making the inclination of the binary system of particular interest to gamma-ray astronomy \carl{[CITE]}.  The inclination is detected as a relative amplitude difference between the two gravitational-wave polarization, such that to lowest order

@@

\noindent It should be apparent that the luminosity distance $D$ and the inclination $\iota$ can be highly correlated in any parameter estimation study, given that both terms modulate the amplitude of a gravitational wave \carl{[QUANTIFY THIS]},

Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance
 and inclination are the worst of the six physically interesting parameters.  Four typical 2D PDFs are
  presented in Figure~\ref{distIotaPDF}.  Notice the large, bimodal uncertainties 
present in some of the 2D PDFs along the $\iota$ axis, due to the similarity between the evaluated
 likelihoods at $\iota$ and $\iota + \pi/2$.  As the majority of the information extracted via parameter 
 estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$ space will be 
 limited, even during the Advanced LIGO/Virgo era; however, there will be cases (such as the first 
 PDF in Figure~\ref{distIotaPDF})  that will prove copacetic to simultaneous measurements accurate 
 enough for coincidence measurements with GRB observers.  Conversely, if a gravitational-wave signal is 
 matched to a detected GRB counterpart, the optical information about the orbital inclination
 will provide an additional constraint on the D-$\iota$ space to vastly improve the results quoted here.

@@

Unlike the mass parameters, the recovery of the position on the sky is highly dependent 
on the location of the source with respect to the detector network in question. 
For the HLV configuration, the three-detector network can only localize signals to one of
two points in the sky.  That is, when using only time-of-arrival information, there is 
equal support in the probability density functions near true location and near the 
point reflected through the plane formed by the three detectors.  See  \carl{[CITE FAIRHURST]} for
 a global analysis of time-of-arrival accuracy for various network configurations, including those considered
 here.

@@

\begin{figure}[ht!]
  \centering
 \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.59]{noisePDF.pdf}
 \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the Advanced LIGO noise curve.  Each PDF represents the recovery of the same $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked at random from the Gaussian colored noise defined by the Advanced LIGO power spectral density.  Notice how the curve is relatively unchanged, but usually assumes a Gaussian PDF displaced from the true value.  This only holds true for glitch-free data, which is an unrealistic idealization when compared to real data.}
 \label{noisePDFs}
\end{figure}

We have performed the current analysis on zero-noise injections for two reason.  First, the results of a zero-noise realization
analysis are identical to those that would be achieved by averaging the results of multiple identical injections 
in different Gaussian noise realizations, as was argued in Section \ref{waveformSection}.  The second reason is simply
that no good model exists for the true (decidedly non-Gaussian) noise that will arrive with a single detection candidate,
Each detection will occur in noisy data, with a specific realization of the PSD provided and with 
possible instrumentation and environmental glitches.  In the case of a unique Gaussian realization
of the Advanced-LIGO noise curve, each realization causes the maximum likelihood of the posterior probability 
distribution to be translated away from the true value; however, these displacements are drawn
according to the zero-noise distribution \citep{Inadequacies}.  Once averaged, the mean
uncertainties should be equal to the uncertainty drawn from the zero-noise runs.

As a demonstration of this, we injected a single $1.4M_{\odot}/1.4M_{\odot}$ system, 
detected in HLVI,  into 5 separate realizations of Gaussian noise colored by the Advanced LIGO PSD, 
and compared the results to the same MCMC recovery in the zero-noise case.  This example
can be seen for one-dimensional marginalization of $\chmass$ and $q$ in Fig. \ref{noisePDFs}.  In effect, the ``real answer'' that will be recovered is a single PDF with similar 
width to the zero-noise PDF, but with the peak likelihood displaced from the true value.

Of course, the largest concern for gravitational-wave parameter estimation will not be the specific
realization of Gaussian noise, but the effects of glitches in the data.  These time-series 
glitches have a variety of well-known and not-so-well-known physical causes in the instrument,
and can cause substantially greater errors in parameter recovery than any specific realization noise realizations.  This has already been addressed for the case of space-based gravitational-wave
detectors (LISA), and is currently being implemented in \texttt{lalinference\_mcmc} 
\carl{[CITE TYSON, PROTO-TYSON]}.

@@

\begin{table*}[t!]
\centering
\caption{\carl{65\% confidence intervals}}
\begin{tabular}{lcccccccccc}

@@

\begin{table*}[t!]
\centering
\caption{\carl{65\% confidence intervals ADD SKY LOCATION SOLID ANGLE UNCERTAINTIES}}
\begin{tabular}{lcccccccc}

\\HLVI\\
\hline\hline
 System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(rad)$& \vline &  $\Delta \delta$   $(rad)$\\
\hline\hline
 $1M_{\odot}-1M_{\odot}$ & \vline & $3.56\times 10^{1}$ & \vline & $2.20\times 10^{-1}$ & \vline & $1.02\times 10^{-1}$ & \vline & $6.22\times 10^{-2}$ \\
\hline
 $1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline & $2.56\times 10^{-1}$ & \vline & $2.60\times 10^{-2}$ & \vline & $2.62\times 10^{-2}$ \\
\hline
 $1M_{\odot}-2.5M_{\odot}$  & \vline & $6.48\times 10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $2.68\times 10^{-2}$ & \vline & $2.87\times 10^{-2}$ \\\hline
 $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline & $1.80\times 10^{-1}$ & \vline & $2.80\times 10^{-2}$ \\
\hline\hline

@@

\hline\hline
 System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(rad)$& \vline &  $\Delta \delta$   $(rad)$\\
\hline\hline
 $1M_{\odot}-1M_{\odot}$ & \vline & $4.34\times 10^{1}$ & \vline & $3.04\times 10^{-1}$ & \vline & $2.53\times 10^{-1}$ & \vline & $1.09\times 10^{-1}$ \\
\hline
 $1.4M_{\odot}-1.4M_{\odot}$  & \vline & $5.32\times 10^{1}$ & \vline & $2.87\times 10^{-1}$ & \vline & $1.21\times 10^{-1}$ & \vline & $1.24\times 10^{-1}$ \\
\hline
  $1M_{\odot}-2.5M_{\odot}$& \vline & $6.13\times 10^{1}$ & \vline & $3.12\times 10^{-1}$ & \vline & $4.68\times 10^{-2}$ & \vline & $7.44\times 10^{-2}$ \\
\hline
 $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.04\times 10^{2}$ & \vline & $3.42\times 10^{-1}$ & \vline & $1.97\times 10^{-1}$ & \vline & $5.77\times 10^{-2}$ \\
\hline\hline

@@

Finally, we reported the ability of advanced networks to constrain the sky location of BNS signals.  It was found that 
the three detector configuration, consisting of the Washington and Louisiana LIGO sites plus the Italian Virgo site,
 was able to constrain all signals with within 50 $deg^2$ on the sky, while the four-detector
configuration, consisting of the three-detector sites plus a LIGO India detector, was able to localize the sky-locations
to within \carl{[QUOTE REAL DEG2 HERE, NOT RA AND DEC]}.

It should be noted that there are two distinct types of systematic error, highly relevant to the gravitational-wave parameter estimation problem, that we have not addressed in this study.  First, we have studied the parameter estimation uncertainties under the assumption that the waveform template we use to recover the signal template exactly matches the fully relativistic waveforms nature provides.  In practice, these waveforms are only approximations to the fully general-relativistic physics required to solve the problem.  See \carl{[CITE]} for a better description of the systematic uncertainties present in the most common waveform families.  Additionally, there are several astrophysical assumptions that can potentially contribute
to systematic uncertainties in the waveforms, such as the neutron-star equation of state, possible modifications to 
General Relativity, etc.

Secondly, as stated above, the noise realization that we have employed here is an substantial idealization.  In practice the noise levels of Advanced LIGO and Advanced Virgo will be highly variable over time, and will \emph{not} be stationary or Gaussian, as is commonly assumed.  Unfortunately, there is no reliable or simple way to simulate the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.  Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here \carl{TYSON WILL WRITE}

@@

\carl{
\section{TODO}
 \begin{itemize}
 \item Discuss the problem of no-spin/how that screws up our ability to constrain masses (BH vs NS)
 \item Be sure to add links to the 1d credible intervals in the abstract, introduction, conclusion, and at the end of each subsection
 \item Also point out how this is a idealization, not an average case (SNR 20 vs reality, again NS vs BH)
 \item Finish adding bibliography/sources
 \item double check the distribution of sources in Distance/Iota; make sure iota is actually uniform in cos(i)
 \item also, check the relative SNRs in each detector for the D-i plots, see if you can tell what's making them double peaked 
 \end{itemize}
 }

>>>>

Within the next five years, the Advanced LIGO/Virgo network will have reached a sensitivity sufficient to enable the routine
 detection of gravitational waves.  Beyond the initial detection, the scientific promise of these instruments relies the 
 parameter estimation techniques being currently developed.  The majority of this effort has been towards the detection
   and characterization of gravitational waves from compact binary coalescence, i.e. the coalescence of black holes and/or 
   neutron stars.  While several previous studies have focused on the parameter estimation abilities of advanced detectors, 
   the majority have relied on approximation techniques such as the Fisher Matrix.  Here, we report the statistical 
   uncertainties that will be achievable, in practice, using the parameter estimation techniques which will be applied to 
   detections of binary neutron star systems.  We find the recovery of the individual masses to be within fractionally within 
   10\% at the 65\% confidence level for equal-mass systems, and within 2\% for unequal-mass systems.
     We also report the average uncertainties on the sky-locations, luminosity distance, and orbital inclinations of randomly 
     distributed sources that can be achieved by different network configurations.
\end{abstract}

@@

Finally, note that the power-spectral density that defines the inner product \eqref{innerProduct} is simply 
the time-averaged sensitivity of a given detector to a specific frequency.  Ignoring non-Gaussian glitches,
 any stretch of data should contain a specific noise realization drawn from a Gaussian colored by the PSD.
   However, what we are interested in is not the parameter estimation that can occur in a specific draw
    from this probability of noises, but the uncertainties averaged over all possible noise
     realizations.\footnote{Similarly to how the Fisher matrix formalism can provide the Cramer-Rao bound averaged over
     all noise realizations} Since our noise model is assumed to be Gaussian, it is unnecessary to recover the
      parameters from a large sample of identical waveforms in different noise; we can simply assume the 
      noise \emph{is} the mean defined by the power-spectral density.  This ``zero-noise'' parameter estimation
       provides a statistical statement on the measurable uncertainties, and is what is reported here.  In Section
        \ref{noiseSection} we provide an example of parameter estimation in several non-zero noise realizations
compared to the zero-noise equivalent \carl{[TYSON WILL WRITE]}.

@@

\begin{figure}[h!]
  \centering
 \includegraphics[trim=1cm 0cm 2cm 0cm, clip=false,scale=0.63]{1414masses2D.pdf}
 \caption{2D marginalized posterior probability density functions for the mass parameters recovered in typical a $1.4M_{\odot}/1.4M_{\odot}$ system.  The posteriors are plotted in terms of parameters used in the waveform, chirp mass ($\mathcal{M}_C$) and the mass ratio ($q$), and in the individual component masses of the binary ($M_1$ and $M_2$).  In the $\chmass$-$q$ space, the posterior would resemble a Gaussian if not for the limitation of $q \leq 1$.  The presence of the $q$ cutoff and the convention that $M_1 \geq M_2$ inform the non-Gaussian features present.  When projected as 1D marginalized posteriors, the component masses resemble the posterior PDFs shown in figure \ref{metaMassPDFs}.}
  \label{1414masses}
\end{figure}

\begin{figure}[h!]
  \centering
 \includegraphics[trim=1cm 0cm 2cm 0cm, clip=false,scale=0.63]{125masses2D.pdf}
 \caption{Similar to Figure~\ref{1414masses}, for a typical $1M_{\odot}/2.5M_{\odot}$ system.  The unequal mass ratio displaces the posterior PDFs from the $q \leq 1$ present in the equal mass case, yielding a Gaussian PDF in both the $\chmass$-$q$ and $M_1$-$M_2$ spaces.}
  \label{125masses}
\end{figure}

\begin{figure*}[ht!]
  \centering
 \includegraphics[trim=2cm 0cm 2cm 0cm, clip=false,scale=0.7]{newMasses.pdf}
 \caption{Mass PDFs for the four BNS systems, averaged over each of the 40 injections.  The average is reported since, in practice, there was quantitatively no difference between the recovered PDFs for different systems with identical masses and SNRs.  Systems with identical mass ratios but different total masses have quantitatively identical PDFs when normalized to the true total mass.}
  \label{metaMassPDFs}
\end{figure*}

@@

To condense the results into a single figure of merit, we average the 1-dimensional mass PDFs into a single 
posterior probability for system.  See Figure~\ref{metaMassPDFs}.  Notice how when averaged and
 normalized to the injected values, the recovery of the component masses depends only on the mass ratio.  
 Furthermore, for systems of equal masses, the posterior barely extends beyond 15\% of the injected values.  
 If one assumes that the threshold between black
   holes and neutron stars lies at approximately $3M_{\odot}$, then it might be assumed that
   the mass recovery would allow one to discriminate between black holes and neutron stars.

@@

\begin{figure}[h!]
  \centering
 \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.75]{distIota2D.pdf}
 \caption{Typical marginalized 2D mass PDFs for luminosity distance $D$ and orbital inclination $\iota$. Notice the bimodal 
 distribution on the first PDF, that can occur when a system is detected nearly ``edge-on'' ($\iota \approx \pi/2$).  In general,
 the degeneracy between distance and inclination forces the PDF into one of these two paths when the system is not edge-on,
  as seen in the second and third PDFs.}
 \label{distIotaPDF}
\end{figure}

Binary neutron star systems (along with neutron star/black hole systems) are one of the best candidates for progenitors of short-hard gamma-ray bursts \citep[and references therein]{Nakar2007}.  After merger, the remnant is believed to emit the burst along the axis of orbital angular momentum, making the inclination of the binary system of particular interest to gamma-ray astronomy \citep{LSCGRB2010,Corsi2012}.  The inclination is detected as a relative amplitude difference between the two gravitational-wave polarization, such that to lowest order

@@

\noindent It should be apparent that the luminosity distance $D$ and the inclination $\iota$ can be highly correlated in any parameter estimation study.

Given this degeneracy, it should come as no surprise that the 2D marginalized posteriors of distance
 and inclination are the worst of the six physically interesting parameters.  Four typical 2D PDFs are
  presented in Figure~\ref{distIotaPDF}.  Notice the bimodal uncertainty 
present in the top 2D PDF along the $\iota$ axis, due to the similarity between the evaluated
 likelihoods at $\iota$ and $\iota + \pi/2$.  As the majority of the information extracted via parameter 
 estimation is from the phase of the signal, the recovery of a posterior in $D$-$\iota$ space will be 
 limited, even during the Advanced LIGO/Virgo era; however, there will be cases (such as the first 
 PDF in Figure~\ref{distIotaPDF})  that will prove copacetic to simultaneous measurements accurate 
 enough for coincidence measurements with GRB observers.  Conversely, if a gravitational-wave signal is 
 matched to a detected GRB counterpart, the optical information about the orbital inclination
 will provide an additional constraint on the D-$\iota$ space to vastly improve the results quoted here.

@@

Unlike the mass parameters, the recovery of the position on the sky is highly dependent 
on the location of the source with respect to the detector network in question. 
For the HLV configuration, the three-detector network can only localize signals to one of
two points in the sky.  That is, when using only time-of-arrival information, there is 
equal support in the probability density functions near true location and near the 
point reflected through the plane formed by the three detectors.  See  \cite{Fairhurst2011} for
 a global analysis of time-of-arrival accuracy for various network configurations, including those considered
 here.

@@

\begin{figure}[ht!]
  \centering
 \includegraphics[trim=0cm 0cm 0cm 0cm, clip=true,scale=0.52]{noisePDF.pdf}
 \caption{The effects of a non-zero noise realization on the recovered PDF for five different Gaussian realizations of the Advanced LIGO noise curve.  Each PDF represents the recovery of the same $1M_{\odot}/2.5M_{\odot}$ signal in a different noise curve, picked at random from the Gaussian colored noise defined by the Advanced LIGO power spectral density.  Notice how the curve is relatively unchanged, but usually assumes a Gaussian PDF displaced from the true value.  This only holds true for glitch-free data, which is an unrealistic idealization when compared to real data.}
 \label{noisePDFs}
\end{figure}

We have performed the current analysis on zero-noise injections for two reason.  First, the results of a zero-noise 
analysis are identical to those that would be achieved by averaging the results of multiple identical injections 
in different Gaussian noise realizations, as was argued in Section \ref{waveformSection}.  The second reason is simply
that no good model exists for the true (decidedly non-Gaussian) noise that will arrive with a single detection candidate,
Each detection will occur in noisy data, with a specific realization of the PSD provided and with 
possible instrumentation and environmental glitches.  In the case of a unique Gaussian realization
of the Advanced-LIGO noise curve, each realization causes the maximum likelihood of the posterior probability 
distribution to be translated away from the true value; however, these displacements are drawn
according to the zero-noise distribution \citep{Inadequacies}.  Once averaged, the mean
uncertainties should be equal to the uncertainty drawn from the zero-noise runs.

As a demonstration of this, we injected a single $1M_{\odot}/2.5M_{\odot}$ system, 
detected in HLVI,  into 5 separate realizations of Gaussian noise colored by the Advanced LIGO PSD, 
and compared the results to the same MCMC recovery in the zero-noise case.  This example
can be seen for one-dimensional marginalization of $\chmass$ and $q$ in Fig. \ref{noisePDFs}.  In effect, the ``real answer'' that will be recovered is a single PDF with similar 
width to the zero-noise PDF, but with the peak likelihood displaced from the true value.

Of course, the largest concern for gravitational-wave parameter estimation will not be the specific
realization of Gaussian noise, but the effects of glitches in the data.  These time-series 
glitches have a variety of well-known and not-so-well-known physical causes in the instrument,
and can cause substantially greater errors in parameter recovery than any specific realization noise realizations.  This has already been addressed for the case of space-based gravitational-wave
detectors (LISA), and is currently being implemented in \texttt{lalinference\_mcmc} 
\carl{[TYSON WILL WRITE]}.

@@

\begin{table*}[t!]
\centering
\caption{Mean 65\% confidence intervals for intrinsic parameters for each of the four systems considered.  We report the confidence intervals of quantities measured, as well as the component masses and total mass.  Although the results for the 
HLV and HLVI configurations are quantitatively identical, we report them separately for consistancy.}
\begin{tabular}{lcccccccccc}

@@

\begin{table*}[t!]
\centering
\caption{Mean 65\% confidence intervals of extrinsic parameters for each of the four systems considered.  As expected,
there exists a substantial improvement in the sky localization capabilities of the four-detector HLVI configuration over
the three-detector HLV configuration.  Note that the solid-angle sky-location confidence intervals, $\Delta\Omega$, are 
calculated directly on the 2D sphere, not by combining the $\alpha$ and $\delta$ uncertainties.}
\begin{tabular}{lcccccccccc}

\\HLVI\\
\hline\hline
 System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &  $\Delta \delta$   $(deg)$ & \vline & $\Delta\Omega$ $(deg^2)$\\
\hline\hline
 $1M_{\odot}-1M_{\odot}$ & \vline & $3.64\times 10^{1}$ & \vline & $2.23\times 10^{-1}$ & \vline & $1.45$ & \vline & $1.48$ & \vline & $1.88$\\
\hline
 $1.4M_{\odot}-1.4M_{\odot}$ & \vline & $5.52\times 10^{1}$ & \vline & $2.56\times 10^{-1}$ & \vline & $1.49$ & \vline & $1.50$ & \vline & $2.26$\\
\hline
 $1M_{\odot}-2.5M_{\odot}$  & \vline & $6.48\times 10^{1}$ & \vline & $2.93\times 10^{-1}$ & \vline & $1.54$ & \vline & $1.64$ & \vline & $2.10$\\
 \hline
 $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.06\times 10^{2}$ & \vline & $2.99\times 10^{-1}$ & \vline & $1.03\times 10^{1}$ & \vline & $1.61$ & \vline & $2.22$\\
\hline\hline

@@

\hline\hline
 System & \vline & $\Delta D$ $(mpc)$ & \vline & $\Delta |\cos(\iota)|$ & \vline & $\Delta \alpha$ $(deg)$& \vline &  $\Delta \delta$   $(deg)$ & \vline & $\Delta\Omega$ $(deg^2)$\\
\hline\hline
 $1M_{\odot}-1M_{\odot}$ & \vline & $4.34\times 10^{1}$ & \vline & $3.04\times 10^{-1}$ & \vline & $1.45\times 10^{1}$ & \vline & $6.24$ & \vline & $5.57$\\
\hline
 $1.4M_{\odot}-1.4M_{\odot}$  & \vline & $5.32\times 10^{1}$ & \vline & $2.87\times 10^{-1}$ & \vline & $6.92$ & \vline & $7.11$ & \vline & $8.35$\\
\hline
  $1M_{\odot}-2.5M_{\odot}$& \vline & $6.11\times 10^{1}$ & \vline & $3.11\times 10^{-1}$ & \vline & $2.67$ & \vline & $4.20$ & \vline & $7.39$\\
\hline
 $2.5M_{\odot}-2.5M_{\odot}$ & \vline & $1.04\times 10^{2}$ & \vline & $3.42\times 10^{-1}$ & \vline & $1.13\times 10^{1}$ & \vline & $3.31$ & \vline & $6.27$\\
\hline\hline

@@

Finally, we reported the ability of advanced networks to constrain the sky location of BNS signals.  It was found that 
the three-detector configuration, consisting of the Washington and Louisiana LIGO sites plus the Italian Virgo site,
 was able to constrain all signals with within 60 $deg^2$ on the sky at the 65\% confidence interval, with an average
65\% confidence interval of $\sim 7$ $deg^2$.  Meanwhile, the four-detector
configuration, consisting of the three-detector sites plus a LIGO India detector, was able to localize the sky-locations
to within  13 $deg^2$ on the sky at the 65\% confidence interval, with an average
65\% confidence interval of $\sim 2$ $deg^2$.

It should be noted that there are two distinct types of systematic error, highly relevant to the gravitational-wave parameter estimation problem, that we have not addressed in this study.  First, we have studied the parameter estimation uncertainties under the assumption that the waveform template we use to recover the signal template exactly matches the fully relativistic waveforms nature provides.  In practice, these waveforms are only approximations to the fully general-relativistic physics required to solve the problem.  See \carl{[CITE]} for a better description of the systematic uncertainties present in the most common waveform families.  Additionally, there are several astrophysical assumptions that can potentially contribute
to systematic uncertainties in the waveforms, such as the neutron-star equation of state, possible modifications to 
General Relativity, eccentricity, etc.

Secondly, as stated above, the noise realization that we have employed here is an substantial idealization.  In practice the noise levels of Advanced LIGO and Advanced Virgo will be highly variable over time, and will \emph{not} be stationary or Gaussian, as is commonly assumed.  Unfortunately, there is no reliable or simple way to simulate the sort of non-Gaussian detector glitches and instrumentation effects that will arise in any advanced gravitational-wave detector.  Since the realization of noise will be the primary factor in the deflection of true signal PDFs from the averages quoted here \carl{[TYSON WILL WRITE]}

@@

\carl{
\section{TODO}
 \begin{itemize}
 \item Finish adding bibliography/sources
 \item double check the distribution of sources in Distance/Iota; make sure iota is actually uniform in cos(i)
 \end{itemize}
 }
